### 2022-09-09 main/chapter_searches.tex
fix many doi links; add cls references

\begin{figure}[tp]
\centering
\includegraphics[width=0.95\textwidth]{figures/seacrhes_fisher_likelihood_binomial.png}
\caption[
Intervals exceeding ratios from the maximum of a Binomial likelihood function,
reproduced from Fisher
]{%
Intervals exceeding ratios from the maximum of a Binomial likelihood function,
reproduced from Fisher~\cite{fisher1956statistical}.
Horizontal lines mark regions where the likelihood function exceeds
$1/2$, $1/5$, and $1/15$ of its maximum respectively.
The extents of these lines could be tabulated to usefully communicate aspects
of its profile.
}
\label{fig:searches_fisher_likelihood}
\end{figure}

\paragraph{Fisher.}
% likelihood
Fisher coined the term `likelihood'~\cite{
fisher1912fitting,
fisher1915frequency,
fisher1921probable
} in the usage that
we employ for the probability of observed data given varied
contexts%
\footnote{%
Fisher used the term `likelihood' for the function exploring
contexts and `probability' for the distribution over
outcomes~\cite{fisher1925smrw}.
We choose the alternative word `prior' for his `probability' since the
likelihood is also a probability, just not a probability \emph{distribution}.
},
and deserves credit for popularising its use in interpreting and communicating
data without the confounding influence of prior probabilities.
In his own words,%
\begin{displayquote}
\small
``%
We can know nothing of the probability of hypotheses or hypothetical
quantities.
On the other hand we may ascertain the likelihood of hypotheses
and hypothetical quantities by calculation from observations%
''~\cite{fisher1921probable},
\end{displayquote}
and furthermore we agree that in comparison to confidence intervals,
\begin{displayquote}
\small
``%
For all purposes, and more particularly for the \textit{communication} of the
relevant evidence supplied by a body of data, the values of the Mathematical
Likelihood are better fitted to analyse, summarize, and communicate
statistical evidence of types too weak to supply true probability statements%
''~\cite{fisher1956statistical}.
\end{displayquote}
For example, Figure~\ref{fig:searches_fisher_likelihood} displays a figure by
Fisher~\cite{fisher1956statistical} that illustrates how data can be usefully
reported by their likelihood's maximum and the regions in which it exceeds
certain ratios relative to that maximum.%
\footnote{%
We use such $L(\check{x})\pm\mathrm{ratio}$ visualizations for
$\pm1\sigma$ and $\pm2\sigma$ error bars on Poisson data in
Figure~7 of~\cite{lester2022hunting}.
When making error bar recommendations, \atlas' statistics committee appears
to have not considered this option~\cite{cowan2011errorbars};
I cannot explain why not, since our statistics experts must surely be familiar
with Fisher's work.
}

@@

\paragraph{Neyman-Pearson.}
\begin{figure}[tp]
\centering
\includegraphics[width=0.46\textwidth]{figures/searches_significant_shrink.png}
\\
\begin{footnotesize}
`So, uh, we did the green study again and got no link. It was probably a{-}{-}'
\\
`RESEARCH CONFLICTED ON GREEN JELLY BEAN ACNE LINK; MORE~STUDY~RECOMMENDED!'
\end{footnotesize}
\caption[
``Significant'' by Randall~Munroe
]{%
``Significant'' by Randall~Munroe~\cite{xkcd2011significant}.
}
\label{fig:searches_significant}
\end{figure}
Figure~\ref{fig:searches_significant}

@@

% p-values
no!~\cite{
schervish1996p,
Cohen1994TheEI,
goodman2008dirty,
greenland2016no,
Amrhein2017TheEI,
Bernstein2016princess,
Trafimow2015ban
}

@@

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=0.95\textwidth]{figures/searches_fisher_likelihood_binomial.png}
\caption[
Intervals exceeding ratios from the maximum of a Binomial likelihood function,
reproduced from Fisher
]{%
Intervals exceeding ratios from the maximum of a Binomial likelihood function,
reproduced from Fisher~\cite{fisher1956statistical}.
Horizontal lines mark regions where the likelihood function exceeds
$1/2$, $1/5$, and $1/15$ of its maximum respectively.
The extents of these lines could be tabulated to usefully communicate aspects
of its profile.
}
\label{fig:searches_fisher_likelihood}
\end{figure}

\subsection{Fisher}
\label{sec:searches_fisher}
% likelihood
Fisher coined the term `likelihood'~\cite{
fisher1912fitting,
fisher1915frequency,
fisher1921probable
} in the usage that
we employ for the probability of observed data given varied
contexts%
\footnote{%
Fisher used the term `likelihood' for the function exploring
contexts and `probability' for the distribution over
outcomes~\cite{fisher1925smrw}.
We choose the alternative word `prior' for his `probability' since the
likelihood is also a probability, just not a probability \emph{distribution}.
},
and deserves credit for popularising its use in interpreting and communicating
data without the confounding influence of prior probabilities.
In his own words,%
\begin{displayquote}
\small
``%
We can know nothing of the probability of hypotheses or hypothetical
quantities.
On the other hand we may ascertain the likelihood of hypotheses
and hypothetical quantities by calculation from observations%
''~\cite{fisher1921probable},
\end{displayquote}
and furthermore we agree that in comparison to other prescriptions
(specifically confidence intervals, to be introduced in
Section~\ref{sec:searches_np})
\begin{displayquote}
\small
``%
For all purposes, and more particularly for the \textit{communication} of the
relevant evidence supplied by a body of data, the values of the Mathematical
Likelihood are better fitted to analyse, summarize, and communicate
statistical evidence of types too weak to supply true probability statements%
''~\cite{fisher1956statistical}.
\end{displayquote}
For example, Figure~\ref{fig:searches_fisher_likelihood} displays a figure by
Fisher~\cite{fisher1956statistical} that illustrates how data can be usefully
reported by their likelihood's maximum and the regions in which it exceeds
certain ratios relative to that maximum.%
\footnote{%
We use such $L(\check{x})\pm\mathrm{ratio}$ visualizations for
$\pm1\sigma$ and $\pm2\sigma$ error bars on Poisson data in
Figure~7 of~\cite{lester2022hunting}.
When making error bar recommendations, \atlas' statistics committee appears
to have not considered this option~\cite{cowan2011errorbars};
I cannot explain why not, since our statistics experts must surely be familiar
with Fisher's work.
}

@@

\subsection{Neyman-Pearson}
\label{sec:searches_np}
\begin{figure}[tp]
\centering
\includegraphics[width=0.46\textwidth]{figures/searches_significant_shrink.png}
\\
\begin{footnotesize}
`So, uh, we did the green study again and got no link. It was probably a{-}{-}'
\\
`RESEARCH CONFLICTED ON GREEN JELLY BEAN ACNE LINK; MORE~STUDY~RECOMMENDED!'
\end{footnotesize}
\caption[
``Significant'' by Randall~Munroe
]{%
``Significant'' by Randall~Munroe~\cite{xkcd2011significant}.
}
\label{fig:searches_significant}
\end{figure}
Figure~\ref{fig:searches_significant}

@@

% p-values
no!~\cite{
schervish1996p,
Cohen1994TheEI,
Amrhein2017TheEI,
goodman2008dirty,
greenland2016no,
Bernstein2016princess,
Trafimow2015ban,
Read2002cls
}

@@

$\cls$~\cite{Read:451614, Read2002cls, ralcls}
